Simulation Study: Null Settings

### 2018-03-30 datasets/simulations/simulations-null.Rmd
Remove unnecessary plots from null sims; fix file names

## intermediary files we create below
gauss_file <- file.path(resdir, "null-benchmark-gaussian.rds")
tdist_file <- file.path(resdir, "null-benchmark-t6.rds")
chisq_file <- file.path(resdir, "null-benchmark-chisq3.rds")

@@

plotsim_average(resdf, met="TNR", filter_set = excludeSet,
                merge_ihw = TRUE, errorBars = TRUE)

>>>>

## intermediary files we create below
gauss_file <- file.path(resdir, "null-benchmark-gaussian.rds")
tdist_file <- file.path(resdir, "null-benchmark-t5.rds")
chisq_file <- file.path(resdir, "null-benchmark-chisq4.rds")

@@
